---
title: "my first markdown file"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
library(dplyr)
library(readr)
library(ggplot2)
```

## Reading the Data
The data displays the class's favorite places to eat. The data also includes favroite dish, price, and the last time the student visited the restuarant. 


```{r}
class <- read_csv("https://raw.githubusercontent.com/URstats/stat209-s18-nicolepiercy/master/fav_restaurants.csv")

```


## Plotting the Data

```{r}
ggplot(class, aes(cuisine)) +
  geom_bar()
```


This plot shows the types of cuisine the class enjoys. 

```{r}
ggplot(class, aes(cost_per_person, yearly_visits)) +
  geom_point()
```


This plot displays the how frequnetly a person visits the restuarant per year and how much they pay on average at a visit.

```{r}
ggplot(class, aes(location)) +
  geom_bar()
```


This plot shows the various locations in which the restaurants are located. 
