---
title: "Lab 09: Annotating Data Visualizations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)

knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)

library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
theme_set(theme_minimal())
```

## Pick a dataset

Today you'll have a choice of three datasets to work with. You can choose
either to investigate Donald Trump's approval rating:

```{r}
trump <- read_csv("https://statsmaths.github.io/stat_data/trump_approval.csv")
```


Pick a dataset (feel free to delete the others from the Rmd file if you would
like), and work on the instructions in the next section.

## Instructions

Your goal in this lab is to construct an interesting visualization with the
data that you choose above. You should make use of several manual annotations
in an effort to tell a visual story about the dataset. Below, you should
eventually provide a few sentences describing what you found in the dataset
and then a single plot illustrating the interesting aspects of the data.
You should incorporate some external information into your plot.

Note that you will certainly want to create many initial exploratory plots
before settling on a final one for analysis. This time, make sure you that you
upload both the Rmd and the html files to GitHub (remember, the final report
should have just one single visualization).

Also note that you will have to use the format `x = as.Date("2017-01-06")` to
add annotations to an axis that uses time as a component.

## Analysis

```{r}
ggplot(trump, aes(date, disapprove)) +
  geom_line() +
  annotate("rect", xmin = as.Date("2017-07-25"), xmax = as.Date("2018-01-30"), 
            ymin = 55, ymax= 58, 
            fill = "red", alpha = 0.1) +
  annotate("text", x = as.Date("2017-10-02"), y = 57.76991, color="dark red", size=8, label="Highest Disapproval Rate") +
   annotate("rect", xmin = as.Date("2017-01-23"), xmax = as.Date("2017-03-31"), 
            ymin = 35, ymax= 52, 
            fill = "green", alpha = 0.1) +
  annotate("text", x = as.Date("2017-02-20"), y = 35, color= "dark green", size = 8, label= "Highest Approval Rate") +
  ylab("Disapproval Rate") +
  xlab("Time of Year") +
  ggtitle("Trump's Rate of Disapproval Throughout Presdiential Term")
            


```

In this dataset, I found that as Trump's presdiency has continued, his rate of disapporval has incresed. This could be due to the increase in decsisions he has made throughout his presidency which were few at the beginning. With few decsions made at the beginning of his term, there are few people to disapprove of his actions. 







